%\documentstyle[11pt]{article}
%\setlength{\topmargin}{-.75in} \setlength{\oddsidemargin}{-.3in} \setlength{\evensidemargin}{-.3in} \setlength{\textwidth}{7in}
%\setlength{\textheight}{9.75in} \setlength{\parindent}{0.2in} \setlength{\parskip}{0.1in}

%\begin{document}

Greetings of the Season!!!!\hfill December 1996


It's over, but I haven't started. You know the resolutions I made on January 1st, 1997, well, I haven't gotten to them so the year can't be
over, can it? Maybe I'll just pretend I didn't make them last year and everyone will think I made all new resolutions this year. (The only
problem is that they are the same ones I've made for the past 10 years and haven't done.) Oh well, I'm always telling my kids that practice
makes perfect. I'll practice keeping resolutions for 15 years and then I'll start keeping them. Either that or I'll just re-word them.!!!!

Nasr, (gonna be 50 this year) has kept several of his resolutions. He promised himself that he would cut down on his work, travel and go on a
sabbatical. He's done and doing it! In order to pay for all the earthquake damage, poor Nasr has really been working 7 days a week 16 hours a
day. (Be smart, get insurance-or you'll pay forever for your mistakes.) Not everything is paid, but a decent dent has been made so at least he
can take one day off and spend time with us. Another resolution was to travel. Of course he makes that resolution yearly because he's gonna do
it whether it's a resolution or not. (I think he does that to make me look bad.) He has traveled across, up and down the U.S., to Greece, to
Egypt, and THREE times to Japan. He's happy to report that this year he swam in the Pacific, Gulf of Mexico, and the Mediterranean. He also just
mentioned that he had a ball travelling. (I thought this was all work related, i.e. he is not supposed to have fun.--Resolution-Send a spy with
Nasr on his trips) It's a good thing he tells me how tired he is of travelling after he comes home, because I can guarantee that I don't have a
ball when I'm home alone with two teenagers!!! His final resolution is that he is going to take a sabbatical this year. Every 7 years he can
take a year off to study and increase his knowledge. As this is his third sabbatical, you know he's been around UCLA a LONG time. He plans to
relax and spend the entire time at his computer writing. (Isn't this what he does when he's working-where is the sabbatical?) He is also going
to be playing Mr. Mom because Virginia has undertaken two full time jobs. I'll send pictures of him in his apron. (Please send aprons in
assorted colors in large sizes. He's always been partial to blue and sometimes ruffles.)

Virginia, (ain't gonna say) is NUTS!! No, its not because I haven't kept my resolutions. No, I'm not going crazy, I'm already certifiably
insane. Do you realize I chose, of my own free will, to go back to school and get my masters IN ONE YEAR!. I'm still working full time and I
have three children and I've lost my extra driver. Work has provided countless hours of overtime without the fringe benefits of MONEY.
Pepperdine is an outstanding university which is exciting, stimulating and exhausting. I'm afraid I may have to resort to using stimulants to
stay awake while I'm doing homework and "overtime." Nasr will be Mr. Mom so I won't have to drive too much and I'm hoping he will prepare the
meals. Now I know why men want to have their wives stay at home. Coming home to an already prepared meal is heavenly. Remember in my letters of
long ago, I craved for the time when my children would be grown and I could have adult conversation-especially when Nasr travels. Well, my
children have grown, but I'm still craving adult conversation. When I speak to Adam especially while he is deeply involved in his computer, his
response is a low guttural grunt with a all right just a second. However, Adam must have developed his own time, because his seconds last for
hours. Jazz is as equally involved with the T.V. She doesn't bother to answer she merely ignores me. She thinks the intercom is meant to be
turned off. Ami, is so enamored with her beau, Mark, that she doesn't even realize I'm talking, so I get no response. So, now you know when you
talk to me, if my responses just aren't right, I guess I just haven't had the practice.

Ami (17, few weeks away from 18) is grown up-sort of-well, she's away at college-sort of-well, she's home every weekend. But, Mom's not
complaining because I do miss her when she's gone. However, as you guessed, Mom's not the reason why she's home every weekend. (It ain't Dad
either.) Ami is attending UCLA (wonder why she chose that place?) and her major is electrical engineering. She has wonderful roommates who are
lots of fun and very supportive. She is taking such advanced math classes that mom panics every time she thinks about it. Also, Ami realizes
that college is just a touch more difficult than high school. When Ami is home there is such a clamor to use the computers. Ami's resolution was
to get a computer. Actually she wanted a car, but I just edited out the parts I can't afford. So, she now took the old pentium to her dorm and
that left the household with only one computer. There are papers to write, e-mail to check on, Internet to surf and games to play. Yes, it is
sad sight to see the family fighting over who is going to use the computer first, but hey Mom did find out that weight is one advantage when you
are fighting for the chair in front of the computer. Maybe Ami should bring the other one back or Nasr should buy another one.

Adam (15) is TALL!! His resolution was to be taller than dad. He far surpassed his resolution. He has stretched to 6'2" and GROWING and eating
and eating and eating and staying so thin!!! I have to say that it is very disconcerting having to look up at your 15 year old. Adam is learning
how to drive. No, he may not drive my new Expedition. He can drive the Oldsmobile or the "Poomobile" as the children not so affectionately call
it. But hey, it's wheels. Adam is very active. He's on a club basketball team and on the high school volleyball team. He has to ride his bike to
school everyday and we tell him that this helps him be better prepared for his sports. He's still not so sure he agrees with us, especially on
cold mornings. Adam has also made an amazing discovery. He discovered that if he puts in a little effort and studies~A's happen! His report card
is proof of his discovery. I also think he very badly wants to get into UCLA and he knows that to get into UCLA you need almost a 4.0.

Jasmine (11 going on 27) is our preteen with a major teenage attitude. She hasn't made any resolutions that I'm aware of but I'm sure when the
time comes she will be very vocal about her resolutions. I'm preparing for "LA NINA" in her teens. I have a feeling that the weather we are
experiencing now is just a prelude to what we will have. (My sisters are all saying-Yes! There is a God! I went through "phases" as my mother
put it and I believe my daughter is going through the same "phases." I think somebody (older sisters) put a hex on me so I would have a child
just like me.) Jazz is into fashion and she lets me know how out of fashion I am. Jazz gets great grades in middle school and is determined to
get straight A's. She's into teen magazines, soccer, art, T.V, T.V, and T.V. She is in the most advanced art group at the Art Conservatory and
she is doing some outstanding work. I keep telling myself she is my artist and artists are always a little moody. (I wonder what my mom kept
telling herself? All I know is that I can "hear" her smile when I complain about my children over the phone.)

I hope this letter finds all of you healthy and happy. Even though the coming year may be filled with trials and difficulties to those close to
us, our thoughts and prayers are with you. Also, with the combined love and strength, we will all weather the difficult times and come out
stronger and better. Have Happy Holidays and a Happier New Year.

Lots of love, Nasr, Virginia, Ami, Adam, Jazz, Lucy (cat), and Butterscotch (dog) Ghoniem


%\end{document}
