%\documentstyle[11pt]{article}
%\setlength{\topmargin}{-.75in} \setlength{\oddsidemargin}{-.3in} \setlength{\evensidemargin}{-.3in} \setlength{\textwidth}{7in}
%\setlength{\textheight}{9.75in} \setlength{\parindent}{0.2in} \setlength{\parskip}{0.1in}

%\begin{document}

Greetings:\hfill December 1999

Another year has come and gone with good times and bad.

Nasr has been the happy wanderer this past year.  He has travelled to many cities in the U.S., Mexico, Denmark, Chile, Japan, Portugal, Spain,
Egypt, and of course China. I have to reintroduce myself to him because he's spent more time in other countries than he has at home.  He has
some fine memories of the trips and he has brought back many pearls of wisdom.  The pearls that were most precious to me, were the black and
corral pearl necklaces from China.  ( No, I am not above using guilt to get my gifts.)  His memories (and you know the over 50 crowd can't
remember much) include walking in the Imperial Palace and on the Great Wall of China, swimming in the lagoons of the Mexican Caribbean, learning
about the fine wines of Portugal, living in a monastery in the mountains of northern Spain, reminiscing with old friends and family along the
shores of the Mediterranean, reliving the horrors of the nuclear bomb in Hiroshima, and most importantly, watching the water go down the toilet
clockwise instead of counter-clockwise in Chile. (He's an engineer so he notices these things.) Yes, these were business trips.  Do you
sometimes get the impression that you are in the wrong business? Things are going well for Nasr, but he is obsessed with "dislocations."  Very
few know what this is, so he desperately needs a hobby.  If anyone has any suggestions (NOT TRAVELING) please let him know.

Virginia is now an Assistant Principal. I actually travelled with Nasr this year. The entire family went to Cancun, Mexico, which was pure
relaxation-just what the doctor ordered.  (At least that's what I told my boss.)  Nasr and I had a second honeymoon in Copenhagen, Denmark.  If
your children visit, make sure they are married and don't watch the television in the hotels.  I learned some new things from the TV and we've
been married for almost 24 years.  Denmark was the first real vacation for me.  My friend took time off to show me around during the day and I
got to do what I wanted.  I didn't have to mediate between the whims and desires of the children.  (There are some advantages to getting older,
or at least having older children because they can take care of themselves for a short time.)  I saw my mother's Danish heritage, (tall blonde
and gorgeous), the Viking ships and a most spectacular view of a red sun high in the sky overlooking the deep fiord.  The California Educational
System thinks educators don't know enough, so I am going back to school again in January to finish Tier II of the Administrative Credential.  I
can't guarantee that all this training is helping me, but I can guarantee that I am going broke paying for my college, Ami's college, Adam's
upcoming college and cars.  We have a new addition to the family.  Frankie is a miniature black lab and loves to love everyone while squirming,
wiggling and groaning.  This is an animal you have to meet to appreciate.  I'm still trying to get Nasr to appreciate him.

Ami (20 on Jan.6) is in her third year at UCLA and is living at home.  Electrical Engineering is a very exciting field, but I feel poor Ami's
only excitement during the quarter are short trips out to dinner. Each of our children is unique, and one of Ami's characteristics is that she
cannot wear shoes to an exam. Remember, Ami is an engineer and must feel free to think. She wears sandals to the exams so she can easily remove
them and take the exam barefoot.  One of her professors used his digital camera and sent pictures over the internet of Ami sitting in the front
of the classroom, barefoot and in deep concentration.  For all of us who do not have a 4.0 grade point average, this might be a strategy to help
us.  Or, it may simply be another Ghoniem idiosyncrasy, but do not poo-poo something that works.  She is working very hard and all the hard work
is paying off.  Ami did her summer internship at Hughes Space and Communications.  She loved it and this gave her the opportunity to find out
what happens in industry.  Of course, since she had to commute the long distance to El Segundo during the summer, Ami needed a car.  Her new,
green, 1999 Honda Civic EX helped her travel to work and to San Francisco at the end of the summer.  San Francisco was an eye opener for her.
She discovered that driving the one way streets with steep hills and crazy drivers was a driving experience she does not want to repeat.  She
did enjoy crepes, Golden Gate park where people were dancing on roller blades, and the area called Haight Ashbury.  According to Ami, there are
a lot of fun shops and interesting people.  As I recall, Haight Ashbury  was filled with "fun" shops and "interesting" people in the 1960's.  It
is scary when your daughter has the same impressions you did, 30 years earlier.

Adam is 17 and is suffering from the dreaded disease "Senioritis."  Ami had it and it only took three years before Adam was infected.  For those
of you who are lucky enough to have younger children, I will describe "Senioritis."  It begins with the attitude that "I know it all and you
can't tell me anything."  Students infected with the disease do not see any purpose in studying because this is their last year and the only
grades that count are your grades from 10th and 11th grade.  They cannot understand why they need a curfew and a curfew of 12:30 a.m. is
"ridiculous" because EVERYONE else can go home when they want to.  They want to make their own decisions and it doesn't matter that they are
making the wrong decisions. They don't need to study for the college entrance exams because it is a "waste of time."   There are three chances
to take the college entrance exams and there is no reason to take it more than once.  "No matter how hard I study, I won't do any better!"  is
the usual response.  They believe if you don't have fun in your senior year, you will never have fun.  They believe a job is more important than
studying for the college entrance exams.  "Who can live on an allowance of \$100.00 a month?" is also a common complaint.   I'm hoping that,
like Ami, this disease will be cured by the time he goes to college in the fall.   Adam had been driving my 1986 station wagon and all cars have
a lifetime and this one just couldn't live through Adam's senior year.  We cried.   Adam rejoiced!  Adam now drives a new, red, 1999 Honda Civic
DX.  The Ghoniems are single handedly supporting the Honda corporation.   Adam is captain of the volleyball team, but he had to suffer through
Homecoming on crutches.  Some people have glass jaws, Adam has glass ankles.  He only has two ankles and I think he has broken five of them. If
anyone has an immediate cure or prevention of senioritis, please tell me because we will be rich when we market it.

Jasmine is 13 and needs an attitude adjustment on a daily basis.  If it could be done, Jazz would have a phone implanted in her brain, or
cosmetically attached to her ear.  Jazz is on the phone CONSTANTLY!!  If you are trying to contact us and no one answers,  Jazz is on the phone.
If she does pick up the call waiting,  please ask if you can call back and leave a message.  Jazz cannot remember your message because she is
too preoccupied with what she is going to tell her friends next.  If you have called and left a message with Jazz, I am sure I have not
responded.  Please call back and trust the machine, not the 13 year old.  Clothes, clothes and more clothes can be seen scattered across the
room, piled high on her desk, on the floor of her closet, and squished into the hamper. One or two might actually be dirty and need washing.
The remainder have been tried on and discarded as too long, gross, ridiculous, un-cool, or "whatever" and left to stay wherever they have
landed.  I was home ill on a school day and by 2:30, I had witnessed her wearing six different outfits. Jasmine has beautiful curly hair that
she straightens daily.  She cannot understand why Mom will not allow her to use chemicals to straighten and highlight it.  EVERYONE ELSE IN
MIDDLE SCHOOL STRAIGHTENS AND HIGHLIGHTS THEIR HAIR!!  Jasmine gave up going to the art conservatory this year.  I hope she will pick it up
again soon, but I will cherish her artwork that I have displayed in my house.

In March, Mom went to join Daddy and now they are together in a much better place.  This is my first Christmas without Mom and I must say I miss
her a lot. Again, I ask if you meet an intelligent, warm, caring and loving person, just smile, remember Mom, and know there are many wonderful
people in this world and we need to take time to appreciate them because they are the most precious gift we have.

This is the end of a millenium and we need to stop and think about what we've accomplished and wonder what is ahead of us.  Let's pray that
it'll be special and enlightening.  Have a Merry Christmas and an even Merrier Millenium!



%\end{document}
