 Greetings of the Season	\hfill				      			December 2005
\vspace{.5in}
      This has been a year of joy, pride and fear.  It’s a quiet Sunday afternoon when I get to write this letter, and as usual I am listening to Christmas carols on the radio, and enjoying a chocolate kiss or two (but who’s counting?).  The difference is that this year, I know Adam won’t be home for the holidays and I am saying an extra prayer for him and all  our young people in uniform who won’t be home either, but WILL be home soon.
      
     Nasr has been to Europe three times in four months, a little bit of Madrid, Prague, Paris and Copenhagen with an excursion or two to Egypt. While visiting Egypt, he discovered Trianon.  It is a Danish bakery established in the 1600’s that recently opened a café just blocks from our home in Alexandria, Egypt.  So this time, Nasr “worked” at the bakery while overlooking the Mediterranean, drinking cappuccinos and eating tasty pastries.  How many people want his job? On one of our joint trips, we stopped for lunch at an airport, and for the first time Nasr was asked for his identification—just to make sure he was old enough to imbibe. He is closer to the big six and yet, this was the first for him.  He looked dumbfounded and it took him a while to realize the waitress was serious. But I think it went to his head because now he spends more time in front of the mirror believing his spot is shrinking.  It’s November and all the new electronic toys have come out and Nasr, as usual, bought the newest toys for himself.  This year he purchased a computer phone.  It is about 3” by 5” and it holds all his contacts, calendar, email, PhD presentations, international presentations—oh, and it also is a phone.  Make Nasr happy and call him on his new toy.  He keeps it turned on all the time, not like previous phones.   818 825-0244.  
     
     Virginia did Sweden!  This year I accompanied Nasr to one of his conferences. (He tries to tell me that conferences are boring.  He’s lying!  They are lots of fun—especially a dinner cruise on a Danish fiord.) While he was actually working during the day, I met Helen Singh and Jean Bacon and we had a Spouses Spectacular Spontaneous Swedish Spree.  The swift ferry ride, the scenic countryside, the immaculately groomed gardens and the gourmet dishes of the fishing villages was capped on the ride home, by the spectacular view from the bridge that overlooks Denmark.  Nasr has never been to Sweden.  Of course, I won’t name all the countries that he has visited that I haven’t—but I have Sweden.  This year I learned that there is one job that is hazardous to my health.  I was washing dishes and  just as I was  reaching to put the clean dishes in the drainer, my back suddenly cramped.  I couldn’t move for days! (Of course, Nasr was on one of his trips.)  It wouldn’t let up so it required many trips to the chiropractor.  Moral of this story—if you don’t want to hurt yourself, don’t do dishes.  Somehow this year Nasr has gotten into the season very early and has purchased my gifts before Christmas.  He has redone our bedroom and for the first time in 30 years, I have a NEW bedroom set.  OOOOH, it is very pretty and very luxurious.  He also bought “me” a new Plasma TV.  If you think that he bought the TV for me, then the diamond that I’m buying next week is for Nasr. (Don’t tell Nasr, it is a secret.)   Besides, do presents that arrive before Christmas day count as Christmas presents?  
     
     Amira (soon to be 26) and Matthew celebrated their first wedding anniversary this September.  One of the benefits of married life is that Amira has become a very accomplished cook.  Almost all of her recipes are from Martha Stewart.  She is addicted to watching the food channel. At least Matt doesn’t have to listen to tales about mom’s cooking, only Martha’s cooking.  They are very active and athletic. (This is why Amira can make these great meals and they both stay so slim.) They run, swim, bicycle and one of their favorite sports is hiking. When Nasr travels these two, very kindly, make sure that I am not alone or lonely.  One Sunday afternoon, they decided they would take me on a hike in Will Roger’s State Park. When we first drove in we saw a lively game of Polo with fast moving horses and flying mallets.  I figured this had to be high class hiking—so nothing too strenuous.  This will be an easy afternoon.  Amira knows that I do not like heights, so she “prepared” me for this hike by showing me the bridge that traversed a canyon that we were going to cross.  I was going to be tough—if I didn’t like it, I could close my eyes and they could lead me across. (Yes, I trust them that much.) Surprisingly, the bridge was a piece of cake to cross.  The unbelievably steep, downhill, limb filled, deeply eroded, foliage covered path was strenuous.  Getting lost eight or nine times, sliding down the bank on my derrière, passing animal skeletons hanging on some old ruins,  swinging Tarzan style on the hanging vines, and traipsing through ankle deep creek water all while “following” Amira and Matthew, the experienced hikers, was exhausting, demanding, laborious and backbreaking.  Amira stayed brave for me.  I stayed brave because it is very embarrassing losing your cool in front of your son-in-law and somehow (hallelujah) we made it out.  Now that Nasr is back, they are talking about taking us both hiking.  Do you think we should go, or just stick to the Polo games?  Amira and Matthew are taking a long vacation (3 months) so they can travel and see the U.S. before they start their new jobs in Washington D.C.  I can talk about it now because they are still only 30 miles away.  It will be a different story when they are 3000 miles away.  But, I will behave like Scarlet O’Hara and I will think about that tomorrow.  I am sure you will hear about it in my next letter. (Look for tears on the paper.)
     
     Adam at 23 is a Marine fighting in Fallouja, Iraq. We don’t get to hear from him very often, but we write a lot of letters.  It has been over two weeks since we’ve heard from him.  I am hoping once the elections are over that things will calm down a bit.  He did learn some Iraqi Arabic and is using it to communicate with the people there.  The part he likes about being there is giving the educational gifts and toys to the kids.  He says the kids are really sweet. Earlier this year, when he was in between jobs because of the uncertainty of going to war, he called me at work to say hello.  Not two minutes later, my cell phone rang and Jazz was on the line.  I was trying to talk to both at the same time. Since neither of them wanted to wait, they both popped the question simultaneously of why they had called.  “Mom, do you have any money?”  Both phones. Both children. Same question.  When you are out of funds, just call the Bank of MOM.  (Yes, I was a sucker and they both got money.)   Adam called several weeks ago with a  good story from Iraq.  He said this was something to put in the Christmas letter.  It gets very cold at night and he and another Marine (both from Los Angeles) had checkpoint duty.  The heater went out and it was really cold.  They do not have coats to wear over their uniforms so they have to find creative ways to stay warm.  Adam said he and his fellow Marine used pieces of an old shack to start a fire.  He used his Boy Scout training to start a fire with no matches.  He didn’t elaborate, but I think he used methods that Boy Scouts don’t use.  The most important part of the story—he warmed up on a very cold night. 
     Jasmine at 19 is attending the local university and trying to decide what she wants to do with her life.    At the present, she is living in a house with three other girls.  Since she cannot afford to be out of touch with anyone she was devastated when her cell phone was stolen.  At considerable cost to Mom, (learn from my mistakes, get cell phone insurance—it is much cheaper), I managed to get her phone replaced.  Now, with a new phone you must put the right message on the phone.  It was a simple message, but it had to be perfect.  She paced as she created the message.  While in the bathroom, the message sounded too angry. So she moved to her room to try it.  No,  it didn’t sound right.  Finally, while sitting in her closet behind a closed door, she voiced her message over and over and over until she got it just right—the right words, the right tone, the right feeling.   Can you imagine what her papers would look like if she put that much effort into making them sound just right?   To keep her company in the house of 4 girls and many visitors, Jazz decided that she needed to get a kitty.  So, she brought home a black cat from the animal shelter and named it “Chicken.”   She has her reasons, but I keep begging her to change the name—she won’t.  I am sure my dad is sorely disappointed in me.    He raised me on a farm and now my daughter doesn’t even know a cat from a chicken.   Now, Jasmine got the cat to keep her company.  However, as there are a lot of people at her house, she was worried about the cat and brought her over here so we could watch her for a couple of days.  Well, the cat, has been here for a month and every time I suggest that Jazz take her home, she kisses me and says, but don’t you like the cat, mom?  Now, I am a grandmother of a cat named “Chicken” who sits on my shoulder like a parrot while I walk around the house cleaning.  
     
     As the year comes to an end and we have to make resolutions for the New Year, let’s all pray for this war to end and that Adam and all the young people fighting in Iraq will come home to a heroes welcome.  Let’s pray that all of them will come home healthy and ready to start the next part of their life.  Let’s pray we all have a great new year and we all will start the next part of our life happy and healthy. 
