
Greetings from the Ghoniems! \hfill			December 2006
\vspace{.5in}

This has been a year filled with worries and wonder.  Things are back to normal—or as normal as it can get in the Ghoniem household.  Many things have happened and I’ll try to bring you up-to-date. 

Nasr had a year of great highs and great lows.  Unfortunately, two days into the year, Nasr lost his mother.  This was a horrible way to begin the year, but his parents have been watching over him to make sure his year turned out great. They really had to watch over him carefully when he was remodeling the house.  Sometimes my dear sweet husband is penny wise and pound foolish. As part of fixing up the house, he needed to trim the trees hanging over the gazebo and in various other parts of the yard.  In his “wisdom” he purchased a chain saw. (Now to most Americans, just the thought of a chain saw fills them with horror.) When Nasr told Adam he was planning to use the chain saw and save \$1500, Adam begged me to convince his dad not to go ahead with his plan.  (Remember, Adam was in Iraq, worried about his father—rather than worrying about the dangers there.) Nasr decided to use the saw himself rather than have the YOUNG and STRONG workers use it. Yes, thanks to their watchfulness, he safely trimmed the 10 trees in the yard.  However, no parent saves their children from danger without a little punishment for their actions.  Therefore, Nasr ended up with such severe shoulder pain from the trimming that the \$1500 he saved on not hiring someone to trim, he paid to the chiropractor to alleviate the pain! Nasr has earned the title “Distinguished” Professor at UCLA.  Yes, it is a great title, but as with most great titles, no money is attached.  He was also elected as a Fellow of the American Society of Mechanical Engineers.  This is a great honor! (You’re right—no money!) After 8 years of hard labor and collaboration with Daniel Walgraef, Nasr completed two books. (1 book 2 volumes and 1100 pages.) Everyone thinks Nasr is the quiet one, but he’s the wordy one in this very lengthy masterpiece.  Now I challenge all our friends to go out purchase this book and try to make sense of it, or perhaps you can use it for weight lifting, because it won’t be a light read!  

Virginia’s year was filled with worry for Adam.  Pray you never have to send your child off to war.  The dye no longer covers my grey because worry totally changed my hair color. (If you think I was bad, Nasr was worse—at least now he has an excuse for his hair loss.) While Adam was away there were not many times to have fun, but I did attend a conference at Universal Studios and I had the chance to walk the RED CARPET.  Yes, I do have pictures and yes it is everything I dreamed it would be.  You feel so special when you walk on the red carpet and hear them  clapping. (Of course it was the Universal employee paid to clap, but, she was clapping with gusto.) This is the first year Nasr and I have actually discussed the “R” word.  At first retirement was something that I feared, now I LOOK FORWARD TO IT!!!  If we play our cards right we can retire when I’m….(Oops,….when I’m seven years older than I am now.)  As soon as Adam was home safely, Nasr and I relaxed and traveled the world. So, I ate paella on my birthday in July in Madrid.  We spent a month traveling in Madrid, Cordoba, Sevilla, Prague, Alexandria, Marsa Matrouh and Cairo.  I swam in the most spectacularly warm Mediterranean waters. Yes, me the hydrophobic swam in the deep water for hours on end. The good news is that salty water makes you more buoyant and some people are naturally more buoyant than others (I’m not telling you why) so I was floating happy.  Now, when I’m in the sun, I always generously slather sunscreen all over my body.  However, I didn’t have it on my lips when I enjoyed 6 or 7 hours in the sparkling, turquoise water.  Within minutes of dragging myself out of the refreshing sea, my lips began to swell and blister.  As I was looking for some sympathy from my husband, he turned and said I should be happy about my very large and sore lips.  He said people pay big money to get collagen in their lips and now my lips were huge for free.  (Do you think he is focusing on saving money because all his “promotions” bring no money?) We decided to travel this winter as well. We used Nasr’s GPS system to get us into the Wisconsin rural wilderness.  The signs inside the hotel rooms warned us against walking the trails because the pheasant hunters might mistake Nasr’s plume of hair for a pheasant.  I have a thing for water this year.  In summer I swim in it and in the winter, I throw it.  My siblings and I managed to change a beautiful pristine snow-covered garden (first blizzard of the year) into a battlefield of freezing snowballs. We had loads of fun, but I forgot my gloves and now my hands are aching with arthritis and pain.  If Nasr tells me the rich and famous put their hands in ice cold snow to shrink the wrinkles, I may send him on an errand through the pheasant filled hiking trails.  Later that same evening, my siblings and I danced and caroused on the dance floor at my niece’s wedding. We all used to wonder why our nieces and nephews were afraid to get married.  I finally realized that it isn’t marriage that they are afraid of, they fear the behavior of their aunts and uncles at weddings. 
									
Amira and Matthew left Los Angeles.  Amira is now working for the state department and for some silly reason she had to move to Washington D.C. to work for the federal government.  I took it quite well.  I only cried for the first 6 months after they told us they were leaving.  By the time they left, they only had to drag me for a few miles as I hung onto the door handle because I couldn’t let go. (Only kidding about the few miles—maybe it was longer.)  Why is it that we encourage our children to do great things and then when they do them they always have to do these great things FAR AWAY from us.  (Don’t remind me that I did it to my mother, because now I know what I did to my parents.  Why do we have to find out the hard way?) Matthew merely moved his office from LA to DC and continues to work for the Aerospace Corporation.  (I tried to convince him to stay too, but Amira had more convincing power than his mother-in- law.) While they were still in LA they took us to Huntington Gardens.  As usual we stopped at the gift shop and they found a book with Shakespeare’s play, Hamlet in it.  As they perused the pages, they decided they would read it to each other.  (Now, to you romantically challenged individuals, that is an extremely romantic thing to do. Hint!) They have a lovely house with a basement and a guest room for visitors.  (Yes, I’ve used it and plan to use it again during the holidays.)  Working for the state department gives Amira the opportunity to hear Heads of State speak.  Well, the back of the head of President Bush was the only thing she saw when he came to speak to her department. Unfortunately, she wasn’t home for the Thanksgiving holiday because her work sent her to Vienna for 5 weeks. I think Amira got the travel bug from her dad. Is there something in the Ghoniem genes that they need to travel and see when the world and use the excuse that they are “WORKING?”  Matthew very intelligently spent two weeks with Amira in Europe.  At first I was worried that Amira would not have a Thanksgiving dinner because they do not celebrate that particular holiday in Austria.  However, Amira, along with several other people, had Thanksgiving dinner at the US Embassy in Vienna. The Ambassador served them dinner on plates embossed with the Presidential Seal. Don’t you feel sorry for her missing Thanksgiving at her moms? 

Adam is home from Iraq safe and sound. (Or as sound as any Ghoniem can be.)  He arrived in April on a rainy morning.  The rain disguised the happy homecoming tears of everyone there.  When Adam got off the bus he was in uniform with his M-16 slung across his left shoulder and his machine gun slung across his right shoulder. I didn’t see the knives and Kevlar but I know they were there when I hugged him.  When he was in Iraq, he had three calendars in his room. He marked off each day three times and then checked the calendar at least four more times during the day as he waited for the day he could come HOME.  After many sleepless days and nights of traveling under cover of night, very sudden takeoffs and quick landings, breathing jet fuel while camped on the runway waiting for his flight out and the excitement of coming home, he was exhausted. It was strange to hug your expertly armed son, but there was so much pride at that unit for all the Marines, and so much relief that these men had come home. Adam doesn’t want to say much about life in Iraq and we may be curious, but we will wait until he is ready to tell us.  Adam stayed at home for a few months and is now living in an apartment and going to school studying electrical engineering.  He is now guarding and checking the points he has on his exams instead of guarding the checkpoints in Fallouja. Nasr feels his son is a genius in higher level math.  He has gone from a Marine to a Mathematician, both require skill, concentration and both will make the world a better and safer place.

Jasmine is awesome—at least that is her description of herself.  And to tell you the truth, I have to agree.  She has decided she wants to be a nurse.  She is taking some very heavy duty biology and psychology courses and (KNOCK  ON WOOD) is doing wonderfully in them.  She likes her classes and she is going to class every day.  When she has an exam she writes on multi-colored note cards and studies from the three inch high stack of notes!  This is a very different Jasmine than the one who used to live here.  So, if anyone sees the old Jasmine, tell her we have the new and improved version at home and we are keeping her. Jazz is exercising up a storm.  She pulls me out the door once a day, then she walks with her friends, and finally she jogs with the dog.  When Jasmine decides to do something, she does it.  My hips, knees and other assorted joints may not like it, but Jasmine is not listening to their complaints and is making us get in shape. One afternoon we were exercising to some very fast music, well I had to grab my upper body to prevent it from making a scene, but Jasmine was too late to grab her pants as they fell to the floor.  I guess all this exercising is paying off if her clothes are falling off!  Jasmine has only taken a few classes toward her degree, but she is already diagnosing me.  I have to say I’m a little concerned especially when she says that because I forget some words, sometimes forget what I was going to do, and sometimes don’t end my sentences, she thinks I have Alzheimer’s.  Now, for all of you who forget some things occasionally, what kind of diagnosis will she make for you?  Jasmine’s cat, “Chicken” keeps me company at night when we are watching T.V., well at least when I’m watching TV.  Nasr is usually snoring on the other couch and the cat is most often snoring in my ear.  I’m afraid to tell Jasmine because she will say I’m going to go deaf from the noise, but then again she’ll say it won’t matter because I won’t be able to remember what it was like to hear.  
I hope all of you will always remember the good times and the laughter throughout each year.  Our family and friends make each year special and we hope to share our happiness with each and every one of you.

Happy New Year!

The Ghoniems
