Season’s Greetings!			\hfill						December 2007
\vspace{.5in}
This has been a year of change, fun, travel, building, buying and it is definitely the year of the animals.
Nasr continues to travel the world.  In just a few days he will be leaving for Nice, France. He complains of being tired, but traveling to France in the middle of a Revolution might rejuvenate him. Nasr is humble and he doesn’t want to talk about the awards and prizes that he has earned over the years. (Believe me, he has quite a few.)  But when he went to Egypt and visited his cousins in the Ghoniem Village, they were extremely disappointed in him.  The neighboring village has a son of a son of a son who has earned the Nobel Prize.  Nasr’s cousins in the village cannot understand why Nasr has not gotten the Nobel Prize.  They think he’s not working hard enough and that he needs to bring honor to their village—the Egyptian version of keeping up with the Joneses—and he needs to very soon get himself a Nobel prize so the village can brag about their son of a son of a son of a gun.  Well, Nasr may not have the Nobel prize, but he certainly has the prize winning ability to bargain.  Once the lease on my car ended, Nasr suggested I drive his Mercedes (great idea for me) and he would drive Adam’s 1999 Civic that had a little run in with another car.  It was drivable, but the door was pretty smashed.  On one of his trips to the hardware store a fast talking, New York accented, young man convinced Nasr that he could fix the dent while Nasr was shopping. It would only cost him \$300.  Now, we all know that is a steal—but remember the adage, you get what you pay for. Nasr agreed. Believe it or not, he still has the car, but it does look a little different.  Nasr came out 20 minutes later and he saw the dent was removed but there were at least 10 bullet-sized holes scattered across the side of the blood-red car.  Nasr gasped, argued, ranted and raved.  He paid the two guys \$20 each and left in a huff.  Now he drives a car that looks like he had a run-in with one of Bonnie and Clyde’s machine guns.  The car can barely get up the mountain to get him to UCLA.  He scurries to get into the slow lanes so he doesn’t get run over. Then once at UCLA, he ducks his head as he enters the parking lot and prays no one sees him.  If anyone has any influence over this man, please convince him that he needs to buy a new car.  We even have space for a new car because Nasr built a shed for all our “stuff” to be stored.  His shed, or as I call it, his “Shedteau” is this beautiful two story barn-shaped building in the backyard.  Most of the stuff is stored in the loft so he made the first floor a “Command Center.”   He has his computers, books, and everything one needs to run a command center.  He spends hours down there. At least he answers his cell phone when I call him for dinner.  He would like to invite all his friends to spend a beautiful day, enjoying the garden while sitting inside his “Shedteau.”  I, however, would like our friends to spend time in our lovely, large HOUSE. 
Virginia—had the chance to travel this summer.  (Ok, so I travel most summers, but this was a wonderful summer.)   I do not know why it has taken so long to get to Italy.  But if you have never traveled overseas, you need to visit Italy.  The history, culture, and romanticism are things everyone must encounter. My favorite city is Sienna.  It is an old medieval town whose architecture hasn’t changed since the 1400’s. Walking hand in hand with the man you love is a special treat, but another is overlooking the green and gold Tuscan countryside.  This sight has been enjoyed by thousands over hundreds of years and it is breathtaking to be part of the hordes that savored the beauty. Nasr, not known for his overt romanticism, really hit the mark on this trip. Not only did we enjoy Italy, but he took me to Paris.  On a busy street corner in the heart of Paris, we shared a chocolate-filled crepe under an umbrella, on a warm summer night, cuddling close to escape the light rain.  I know I saw lots of sights, but that was the moment I will always remember. I can hear my children eeewwwing and cringing.  This is not something they wish to imagine, but to those in my generation, romance at 60 is still possible.  We also walked the Downs in Kent, England—more romance.
Amira and Matthew are still living in the Washington D. C. area.  And they love it!  (Darn—I thought the cold weather would have sent Amira packing and coming back to Los Angeles.)  She did have some concerns with the cold, however.  Amira washes her hair and then drives to work with her hair still wet.  The day of the first freeze however did give her some cause for concern.  She was not worried about driving on icy streets, she was worried that her wet hair would freeze, break and then fall off.  To her happiness, she is not walking around with short little curls on her head.  Matthew and Amira have jobs that are exciting and fulfilling.  She and Matthew love to run and hike.  They’ve seen a black bear on their hikes and Amira has run over 100 miles in a month.  (How long would it take her to run home to Mom?) They live in a 50’s vintage home and there are some unwanted creatures who love to venture into warm spots.  Being the Knight in Shining Armor that Matthew is, he set some mousetraps before he went off to fight the good fight in the far off land of Florida. (Translation—he had to travel for work.)  Before Amira went to work, she went down to the laundry room and she spotted a mouse in the mousetrap.  She was in too much of a hurry to remove it then, so she waited until after work.  Now, on the way home she was mulling over in her mind the myriad of ways to remove a mouse from a trap. (That is the job of the Knight and she had never done it before.)  As she pulled open the laundry room door, she gasped.  The mouse and trap were gone.  This is good news and bad news. Choosing to focus on the good news that she didn’t have to touch a dead mouse, she bent to take clothes out of the dryer.  Suddenly, something rubbed up against her foot.  EEEEEEK.  Yes, it was the mouse AND the trap.  Both ran. Amira pounded up the steps and the poor mouse went pitter patter thunk slap, pitter patter thunk slap as it dragged the trap behind it.  Amira, remembering that she is an engineer, grabbed the ancient tool to remove mice, a broom.  She chased the mouse with the broom with little success.  Finally, she devised a larger trap.  She opened a large paper bag and in one quick sweep swished the mouse and trap into the bag.  She now hopes that the mouse will escape the bag after it gets to the dump.  May I give a mother-in-laws suggestion to the Knight—don’t set traps when you are going off to fight the good fight.  For their 3rd anniversary, they traveled to Italy.  They couldn’t resist after mom and dad bespoke of Italy’s virtues for days on end when we visited their lovely city of Falls Church.
Adam—is now a proud homeowner.  He has purchased a two bedroom condominium with a loft and a balcony in Canyon Country.  Now he has to furnish it from the ground up.  He is lucky that he has a father who is very generous and who likes to fix things.  Adam will be in for a rude awakening when he realizes how much upkeep a home entails.  I will let you know next year how well he is handling his new acquisition. Acquiring things is what my children do quite well.  Considering that Adam is moving into a large spacious area he figured he would be clamoring around by himself in this two bedroom condo so he decided he needed a companion.  Adam is a muscular, six-foot two-inch, Marine who is studying the boxing art of Muay Thai.  So you can imagine the type of dog that Adam would bring into his home.  Well, you wouldn’t be right.  He has purchased a Toy Fox Terrier. This little bouncing, big eared, long-legged, four pound circus creature barely comes up to Adam’s ankles.  Don’t ask me how this minimal dog got the name of Maximus (Max). He is great fun with which to cuddle and play.  Adam’s greatest challenge is potty training.  Do not say my children are fools.  He is potty training his puppy at my house so when he finally moves into his white carpeted home, all the accidents will be over.  Also, I find myself babysitting for a crying puppy when his dad is out.   Adam is continuing to take his electrical engineering classes.  We are hoping that they will not be interrupted again, but his Marine Unit is scheduled to go back to Iraq this coming November.  If there ever was a time to wish for peace on earth, this is the time.  
Jasmine (Jazz)--cannot hide her glee that Adam is moving out and she will be the center of attention and she will get the biggest room in the house. (We offered her two small ones, but she wouldn’t take them.) Now, mom has two rooms and she happily has plans for them.  But she will have to get a lock on them so they do not become dumping grounds for any excess junk that Jazz doesn’t want in her room.  Jazz is taking tough chemistry courses and doing well. Of course, she does have two tutors at her beck and call.  (Nasr and I wonder how old we will be when WE can actually get out of college and STOP STUDYING.) If any of our friends miss the old college rah-rah, the stresses of exams, and the long, tedious, hours of studying, just give a call and we’ll gladly step aside and let you take over.  We lost two cats this year (Lucy lived to 17) , so Jazz couldn’t stand the fact that we only had one cat, (named Chicken—and she is) in the house.  To our surprise, only a couple of days after the appearance of Max, Jasmine brought Lola home.  Lola arrived feeling pretty sickly  and our daughter has been practicing her nursing skills on this little, grey and white, scruffy kitty.  Nasr’s expression was not one of pure happiness.  He feels that the animals are pushing him out of his home. (He may have a point there.) There was a lot of grumbling, mumbling, arguing and then cooing and ooing when he finally saw the darling little Lola.  I am trying to convince him that all these animals may be our only grandchildren.  So we better enjoy babysitting—it’s easy at this point.
	I want to wish everyone a Happy and Healthy New Year.  Let’s pray for peace and the safe return of all our boys and young men fighting for our country.