Happy Holiday Greetings!		\hfill						December 2008
\vspace{.5in}
	As usual our year has been filled with fun, fruitful and sometimes frightening times, but, we have come out unscathed and ready to reminisce on the year and to tell yet another story.  Now, with computer in hand (ok, on my lap) and Christmas music echoing through my earphones, I’m ready to tell the tale of the Ghoniem family.
	Nasr cannot deny his age or even hide it anymore.  In October, friends and former students staged a symposium in honor of his 60th birthday in Tallahassee, Florida.  Nasr was supremely honored by the number of people who attended and many flew in from across the globe. Even after all these years, he still insists that attending a conference is work, but whenever I go, there is a lot of laughter, scrumptious meals and wonderful, stimulating, conversation with great friends.  If this is what you do at work, I want your job. Speaking of work, Nasr, unfortunately, did “work” while we were on our summer vacation.  However, teaching has now taken on a different look.  He taught an online class which required hours of advanced preparation including sitting in front of the camera at UCLA and presenting 40 hours of lecture.  Now, fast forward to our summer vacation and picture yourself on the Red Sea off the coast of Egypt.   Imagine turquoise and royal blue waters lapping over beautiful red reefs and in an about those reefs are fish of purple, yellow, green, and blue hues.  Each creature, both large and small, has unique patterns of stripes and spots. (They assured me that there are no sharks in this area—I didn’t see any sharks, but we were snorkeling in the middle of deep water with no land in sight.) The sound of the water lapping against the reefs is so peaceful; yet watching the wildlife is exhilarating, particularly if you are watching for sharks.  Now, as soon as Nasr finished his snorkeling and was sitting on the yacht with nothing to do but watch fish jump from the rippling  sea he pulled out his trusty iphone because he was working!   No one really knows the power of these little gadgets until you are in the middle of the Red Sea.  You expect to feel the gentle rocking of the boat, the powerful warmth of the sun beating down on you, but you don’t expect you will have the power of the Internet.  While I’m gazing across the blue expanse, Nasr is emailing his students from his class and answering their questions.  He is teaching and providing the support they need from his “classroom”.    Now, with his iphone, Nasr’s classroom can be anywhere—on a yacht in the middle of the Red Sea, or in a gondola on the narrow waterways in Venice.  But I must admit technology did not help us in all cases, particularly when the hot Santa Ana winds blew over California and ignited the mountains and hills behind our house into a fiery inferno.  I must admit our hearts pounded in fear when we were awakened at 4 a.m. by police sirens and the tinny sound of the police officer shouting through the loud speaker, “Mandatory Evacuations!  You must evacuate your house immediately.”  What do you take?  The P’s—pets, papers, prescriptions, pictures and people!  The cars were filled with “necessary items”(ok some jewelry is necessary too, even it is doesn’t start with P) and we drove down the street watching our neighbors packing  their cars, all of us not knowing if we were coming back to our homes or not.   What do you do when you are stressed and temporarily homeless?  Well, for Nasr, he goes shopping.  What does he shop for?  He shops for computers—remember “computer” doesn’t start with a “P” so it wasn’t packed.  Ok, I lied. You know Nasr doesn’t go anywhere without a computer, but he took my computer by mistake.  Since we couldn’t get back into the house, he purchased a computer that he can take anywhere.  So, when you see his 6 inch by 9 inch little blue computer, you know he got this during the evacuation.  Remember, when Nasr travels, size does matter.  Thank God, the firefighters performed their daily miracles and we were able to get back into the house later that evening. 
	Virginia has a long, long, long way to go before she is anywhere near Nasr’s age.  I just wanted to make that very clear so no one has any misconceptions.  This year, along with all our other travels, we are re-discovering Los Angeles.  We may not be teenagers anymore, but we love to go bicycling along the beach and enjoy the spectacular ocean view with fiery sunsets and cool breezes. We each listen to our ipods as we bicycle past the hot sand and the breaking, thundering waves.  Our only problem is synchronizing our speed.  We have the same music, but the shuffle mode means that sometimes I’m listening to classical music and rolling at a relaxing speed, while Nasr is listening to the fast-paced, belly dancing, rhythms and it is obvious he is pedaling to keep up with the shimmying hip swings of the dancer.  When he listens to the love ballads of the 70’s and s-l-o-w-l-y reminisces, I’m listening to the 60’s beat of the Beach Boys and my wheels move like I’m riding fast rolling waves.  We bicycle a distance of about 15 miles and are fortunate to travel through the colorful city of Venice, California.  It is here that we must carefully dodge and avoid the city’s  assortment of street entertainers, artists using a variety of media from henna to silverware, and young bikini clad ladies, each more beautiful than the next, skating on fast moving roller blades. I try not to be jealous, but Nasr had a near collision with one of the young ladies, and I am desperately trying to convince myself it was not intentional, it was merely that he was staring at the other more scantily clad girl and didn’t see the one merely wearing short shorts. Nasr blames it on Pavarotti—he says he was focusing on the power of Pavarotti’s voice and his feet were simultaneously powering along and he just didn’t notice the world around him. Now, you know why Nasr is so willing to get his exercise at the beach.  But, the beach is not only for exercise, we do want to relax.  I suggested Nasr take a book to help him relax. However before we go, I do need to check his backpack, because the first time we went he planned to “relax” with a book that teaches C++ , the computer programming language.  I informed him that this book was not recreational, nor relaxing.  Finally, I convinced him to take a magazine to read.  Ok, the front cover of the magazine spoke of economic ruin for the world, but you have to realize that this is relaxing for Nasr.  Not only have we relaxed in Venice, California this year, we also made a sojourn to relax in Venice, Italy.  You must visit the beautiful, narrow, winding streets and canals and enjoy the romance of the city—especially a gondola ride.  Yes, Nasr held my hand lovingly while the gondolier sang in the beautiful black and gold gondola while we silently floated through the narrow, ancient canals. (My kids are eewwing right now.)    On our way to Egypt this year, we stopped in Venice, Vienna, Salzburg, Bratislava and Budapest. The highlight of Austria for me was the high winding mountain ride to Salzburg. For four hours one way we listened to Mozart and enjoyed one spectacular mountain view after another. (Nasr decided he never wants to hear Mozart again after listening to 8 hours of non-stop Mozart.)  Ok, we took a rather circuitous route on our way to Egypt, but if you are going to travel, never travel in a straight line.
	Amira and Matthew are living in Falls Church, Virginia and love it.  I was hoping that the cold weather would scare Amira and bring her back home, but she is tougher than the icy weather.  Actually, it is her job with the opportunity to travel that keeps her in the area.  Amira is definitely following in her father’s footsteps.  Just like her dad, she has done a lot of traveling this year.  Her travels have included a couple of trips to Israel and a trip to London, Australia and New Deli, India.   She is two up on her father because Nasr has never been to Israel or India.  She tells us tales of the beautiful white marble Taj Mahal with its colorful history of intrigue, love, and betrayal.  The streets of India are a maze of cars, bicycles, “took-tooks,” huge semi-trucks, pedestrians and cows!  She is amazed how anyone can actually get to their destination, but she assured us they all do.  She was particularly astonished by a row of cows that stood perpendicular across traffic. Somehow, the cows crossed the street unharmed and then patiently  stood in front of different vegetable vendors and restaurants waiting for the owners to feed them before moving to the next door.   Of course, she didn’t leave Matthew behind all the time.  Together they went to Nice, France.  Warm weather, the blue Mediterranean and the one you love.  It couldn’t have been better—well, maybe a little longer, but not better.  Creativity is still Matthew’s middle name, so while working and attaining a great promotion; he also created a beautiful sculpture for his parent’s garden.
	Adam started the year off sparkling-well at least he started by giving Oanh a sparkling diamond.  So, at the stroke of midnight, he and Oanh were officially engaged.  (His father needs to look at the rock and learn—I’m proud that Adam knows how to pick out a beautiful stone.  Remember, a mother’s pride is different than a father’s.)  Adam is now a home owner and has learned the trials and tribulations of dealing with a broken garage door opener,  the washer and dryer gas hook up problems, plumbers, and a mortgage.  He has also found it isn’t all bad; he also gets to enjoy the heated pools and tennis courts.  Nasr and I took Oanh and Adam to the beach with us to enjoy kite flying and swimming in the ocean.  Nasr was really feeling his age and gravity when Adam showed off his muscular physique.  Adam has been working out and his biceps and calf muscles are huge testimonials to how hard he has been training.  Poor Nasr took one look at Adam’s muscles and you could see he was totally deflated (and it was obvious his muscles were too) but Adam convinced Nasr that he would help Nasr get back in shape.  Adam also got the travel bug from his dad.  His travels however are more domestic because he wants to see his great country.  He’s been to New York and Washington D.C.    However, starting in January, the Marines are preparing to send him and his unit of Marine Reserves to Afghanistan.  When he is finished, Adam also will have traveled to two countries that Nasr hasn’t visited, but unfortunately, it hasn’t been by choice.  Once this tour is up—Adam will be finished with the military and he will focus on his future.
	Jasmine completed her Associate of Science degree and is at this moment filling out applications for nursing schools.  She has applied to 17 schools and we will know by this coming April what school she will be attending.  So obviously she has been studying very hard and our dinner conversations revolve around phrases like “electron capture, beta emission, neutron decay, N over Z, and positron emission.”  Now for the non-nuclear chemistry aficionados, you may feel left out and a bit confused.  Don’t worry; I definitely was not a part of that conversation.  And now I know what it means when they say, it was all Greek to me.  To help prepare for her career, Jasmine has been volunteering at one of the local hospitals.  She can hook up heart monitors, move patients from bed to gurney and back and she proudly makes even the grumpiest patients smile. Jazz has two cats, Mortimer and Chicken.  As everyone knows, with animals, comes the responsibility of cleaning up after them.  However, Jasmine believes that really isn’t a part of her job description.  However, Mom and Dad insist if she wants money, she must clean up after the cats.  One Saturday, when the odor was particularly overwhelming we again demanded she clean it up.  So, as any well prepared nurse, she donned her surgical gloves and lacking a surgical mask, she had to improvise.  She covered her nose with a gauzy, fruity designed paper towel.  She secured it behind her ears and tucked the top under her glasses.  She gingerly picked up the litter box and held it at arm’s length.  She pushed open the garage door with her backside and as she turned around the gardener approached from the yard.  Jasmine, dressed in her Dr. Frankenstein surgery gear, looked at the trash can helplessly, willing it to open up.  The gardener was a complete gentleman and graciously opened the trash can.  Please remind me that I owe him a huge tip for not laughing uproariously at my daughter.  But, believe me, he had a great story to tell when he got home.  Jasmine will be a great nurse, and I wish I had a picture of her in her litter cleaning gear to put next to her nursing diploma.
This historic year has come to an end, but history is still in the making.  So many good things have happened and will continue to happen. Pray Adam comes back safely—or maybe even better—pray for a Christmas miracle or a January 20th miracle and that things will change and he will not go.  I will not let myself feel down and sad about the world. As you can see, the world shouted for joy in November and it is this pure joy and happiness that I wish for everyone.  Have a Happy and Healthy New Year.							