Season’s Greetings, 	\hfill						December 2010
\vspace{.5in}

It’s just Nasr and I in the house this cold December morning –it is a freezing  63 degrees.  Remember, winter looks different in California .This year has been filled with new opportunities, new beginnings, so many memories and lots of joy.
Nasr—now considered a senior citizen—has had several job offers across the world.  One offer he is taking quite seriously is an opportunity to help start up a brand new university in Abu Dhabi—yes that very wealthy city state on the Arabian peninsula. We flew first class and didn’t feel the 18 hour trip. We stayed in Shangri-La—yes , it was a magical place and palace—lots of Indian food, and exotic Indian music—remember India is just a stone’s throw across the Arabian Sea.   We would live in ultimate luxury 25 floors above the vibrant blue sea with a view of the palace and an old city growing into a modern metropolis.  Oh, the job is going to be very exciting and extremely demanding on Nasr’s time.  However, two important things are missing—our wonderful family and friends.  Both Nasr and I are trying to eat a little healthier, but  I think Nasr takes the need to eat healthy to a new extreme.  He loves the all you can eat salad restaurants—you know as well as I do, that there is a lot more than salads there.  There may not be a lot of protein, but there are tons of carbs.  So, we were walking into the restaurant and Nasr kept hiking up his trousers.  He grinned sheepishly and quickly admitted that he wasn’t wearing a belt so he could eat as much “salad” as he wanted and wouldn’t be uncomfortable.  Isn’t the purpose of a salad bar to eat less?  Nasr has read the research and knows that we have to keep our brains active to prevent any unwanted memory loss.  So, he has taken up chess and he plays it every night before he sleeps on his iphone. Oh, he also plays it every time he gets a chance, so don’t assume when he opens up his ipad or iphone that he is working, he is most likely playing chess.  Now, Nasr hates to lose, so it is really important that computers have an undo button—which he uses often.  He has to win.  He sets the level of difficulty carefully so he assures his win.  He cannot sleep until he hears the computer shout “hooray!!!”  Once I hear the cheer, he happily  turns off the light and sleeps soundly.  

Virginia loves being “Teta.”   That “G” word that ends with “ma”  gives me a little difficulty.  When I look around and see a grey haired little old lady, she is a grandma—me, I’m a Teta.  This summer I had a chance to visit my amazing granddaughter and then again during the week long Thanksgiving break.  It is fantastic having all the fun and none of the responsibilities!!!  Why didn’t I do this earlier—oh yeah, my kids had to have kids first—no pressure kids—but I like being Teta.  We did travel this summer and we went down under to Sydney, Australia.  When you look at a map, that continent/country is truly tucked under the lower half of the globe.  Well, when you walk in Australia—you are truly upside down—and gravity has to work very ,very hard to keep you on the ground.  I could feel gravity at its best.  My calves and legs ached from the pull of the gravity.  Now, some of you may be raising your eyebrows, but I swear I could feel gravity holding me down and it told me I had to lose some weight before I go back or my legs won’t be able to handle the gravity of the situation.  In spite of the triple dose of gravity, Australia is beautiful and the people are warm, kind and funny.  We saw the Blue Mountains, called so because the eucalyptus trees secrete an oil that gives the mountains a bluish color.  I held a koala, petted a kangaroo and a saw herds of them in the wild—no I did not pet a wild one.   Many people thought we were crazy to travel one week before our huge summer event, but the event of the year went off without a hitch.   You know how difficult it is to find the perfect dress for special events.  Well, I found a pastel green gown that looked “pretty.”  As we were driving home, Jasmine suggested that in order to make the dress look a little better on me, as I looked too pale in the dress,  she could find a place that would paint my skin a little darker so the dress would look better.  Paint my skin? Who changes the color of their skin to match a dress?   Needless to say, I returned the dress and got a vibrant blue and no, I did NOT paint my skin.

Amira, Matthew and Siena (15 months) are a very active family.  Siena ran her first 5k run in October. Not too many one year olds run races, but she is an awesome granddaughter.  Ok, I will fess up, Siena didn’t use her legs—she sat comfortably in the stroller while mom and dad ran in the truly cold weather—they live in Virginia.   While they were visiting in August, Siena wasn’t quite walking, but she got around very well while hanging onto grandparents, aunts, uncles, mom, and dad.  All the adults needed Ben Gay for their aching backs, but she had a chance to explore the house, backyard and get up close and personal to the cats and dogs.  Siena is talking up a storm.   I think her first words after dad were cat and dog.  I’m not sure she knew the difference between the two since Adam’s dog is smaller than a cat.  Now, she has quite an extensive vocabulary.  When asks what a tiger says, she uses her deepest voice to say “ AAARRRR”. Siena is very outgoing and loves to say “hi” to anyone who passes by.  Both Amira and Matthew got promotions this year.  I wonder if the promotions are directly related to the amount of traveling they both do?  Amira and her father are in a competition about who will travel the most each year.  She always envied her father the amount of traveling he did, but now she is finding that there is a real downside, she misses Siena. 

Adam—the day I am writing this letter is exactly one year to the day that he returned from Afghanistan.  I cannot tell you how happy we are that he and his unit all returned safely.   I don’t think too many people accomplish as much as he has in one year after being at war.  (Does it sound like mom is proud of her son?)   He went back to school and has taken very difficult electrical engineering classes for two semesters very successfully.  Adam’s ingenuity has helped him get out of sticky situations, but this year, he helped his dad with a sticky situation.  While getting gas on the way to the airport—Nasr always is running late—he put the credit card in the gas pump, but the pump wouldn’t release his card.   He could see the tiny edge, but it was impossible to get a grip on it.  Quick thinking Adam, asked for a piece of gum (he knows mom always carries gum)  chewed it quickly, took it out, stuck it onto the  tiny portion of the protruding card and in seconds, the card was in his hand and moments later Nasr was on his way to the airport and didn’t miss his flight.  Just call him Ghoniem McGyver!   Well, the best part of the year—for mom—was Adam’s marriage to his high school sweetheart, Oanh Hoang.  Adam and Oanh have been together for over 10 years.   Adam is so lucky to have found and kept such a wonderful young lady and of course, mom thinks Oanh is pretty lucky to have stayed with Adam.  Now, you must realize that the military requires the young men to shave every day—even in the worst of conditions,  so when Adam returned, shaving was one thing he rebelled against.  By mid July, he looked a lot like Grizzly Adams—all beard and not much else.  We did convince him to shave about two weeks before the wedding.  It was a good thing that we did because when he shaved, his face looked like a slice of Neopolitan ice cream.  His forehead was dark chocolate brown,  his nose was sunburn from too much fun at his bachelor party rafting down the Kern river, and his chin was vanilla white where his skin had not seen any light under his heavy beard.  Oh, the rafting party was fun, except my nephew, John, decided to go rafting down class 4 rapids without the raft.  Thank God he got out safely! August 1, 2010 was a day of celebrations from three different cultures.   The morning started out with the Vietnamese Tea Ceremony.  Oanh, her sisters, and family were dressed in the beautiful traditional dress—the “awsai.”  Oanh also wore the traditional headpiece that only brides wear.  To add to the color of the day, Adam wore his Marine Dress Blues.  Seeing Adam in his uniform, knowing he has only been home from war for 8 months, was very emotional for both sides of the family.   This was the ceremony where there were many tears of joy, happiness and relief.  I feel blessed that my family could experience the beauty of the cultural exchange.  Oh, and the food flowed from everywhere and it was very scrumptious.  Later in the day, Oanh rode to the second ceremony in a white, horse drawn, carriage.  She was more beautiful than any Cinderella as she walked down the aisle to meet our son styling in his tuxedo to participate in the Egyptian Islamic Ceremony officiated by Adam’s “Uncle.”   Finally, the Hawaiian officiant from the good, old US of A, made it completely legal in the state of California.  Of course, the Ghoniem wedding was not complete until the Russian belly dancer, wearing a candle topped headpiece, escorted the bride and groom into the room.  Adam and Oanh danced with her and everyone danced the night away.   The day passed much too quickly for mom, but Adam and Oanh were anxious for the three week honeymoon in London, Paris and Rome to begin.  Their favorite city was Rome—I know they will return.  They are now living in Canyon County, in their newly remodeled condo.  Their address is 18183 Sundowner Way \#848 Canyon Country, California.  91387.  

Jasmine –my baby—at 24—is living in San Diego and attending the University of California, San Diego (UCSD).  Now I always want the best for my children, but as I recall my college apartment was old, dingy, and had the view of the neighbor’s junk-filled driveway.  Jazz’ apartment is bright, airy, well furnished, (thank you parents) and has a view of the mountains and canyons.  In this gorgeous apartment, she has a “no shoe policy” to help keep it clean.  Why is it when the kids move out they start to be mindful of their things and their surroundings? Why can’t they start when they are in high school?  I think that is how Nasr developed his stoop, bending down so often to pick up after children.   To keep her CLEAN apartment cozy, she has Mortimer her cat and has now adopted a new “child.”  Dexter is a rust-colored, fluff-ball that loves to rough and tumble.  Pretty soon we will start calling Jazz the “cat lady.”    Jazz does have interesting décor in her home.  Every window, sliding glass door, even the refrigerator, any flat surface that can be written on with a dry erase marker is covered with chemical formulas such as glycolysis.   The balcony door has the break down from the six carbon ring into three carbon molecules running from the top of the door to the bottom.  I asked her to explain her bio-chemistry to me.  She just shook her head and said a little impatiently, “Mom, I think this is too complicated for you.”    Word of advice for young parents, never let your kids know your weaknesses, because your children will remind you of them, often!  All of YOU who can do bio-chemical analyses in your head, please let me know—I suggest you have a bio-chemical conversation with Jazz. 
2010 has been filled with adventure and joy.  Each time our families gets together, I thank my parents for the most precious gift they could have given me—my siblings and the laugher and happiness that we share when we are together.   My prayer is that everyone is blessed with wonderful family, unending fun and happiness, and most importantly, good health. Oh, and by the way, to finish the story, Nasr and I decided, there is no place like home and we are NOT moving to Abu Dhabi.   Have a very Happy New Year!!!
